\mythesistitleNOTSYNPOSIS

### 2012-01-06 src/020chap2.tex
trivial commit before pushing

\temptext{
  \begin{enumerate}[ -I-]
  \item  Variations - PQR, PC etc. [MM96, Hsu01, McC04]\\
    PQR trees is a generalized data structure based on PQ trees
    \cite{mm96,mpt98}.  \cite{tm05} describes an improved algorithm to
    build PQR
    trees. \tnote{improv in terms of what?}.\\
    Generalized PQ trees McC04 - brief. Will be elaborated in
    Section~\ref{sec:surveycertalgo}\\
    Hsu also invented PC trees \cite{wlh01}\tnote{This result first
      appeared inproc ISAAC92} which is claimed to be much easier to
    implement.
  \item Set theoretic characterizations [Hsu02, NS09]\\
    \cite{wlh02} describes the simpler algorithm for
    COT.\tnote[pressing]{in terms of what?}\\
    \cite{nsnrs09} describes a characterization of consecutive-ones
    property solely based on the cardinality properties of the set
    representations of the columns (rows); every column (row) is
    equivalent to a set that has the row (column) indices of the rows
    (columns) that have one entries in this column (row). This is
    interesting and relevant, especially to this thesis because it
    simplifies COT to a great degree by reducing the solution search
    space owing to the a simple set theoretic characterization.\\
  \item Parallel algorithms [AS95, BS03, CY91]
  \end{enumerate}

>>>>

After the invention of \PQtrees, there has been several variants of
the same with either simpler procedure of construction, like \PCtree
\cite{wlh01}\endnote{First appeared in
  \cite{wlh92_isaac}.\tnote{check}} or a generalization of it, like
generalized \PQtree \cite{mcc04}. \PQRtree is another generalization
of \PQtree by \cite{mm96,mpt98}. There algorithm was improved by
\cite{tm05} \tnote{improved in terms of
  what?}. % describes an improved algorithm to
% build PQR trees.

\temptext{Expand a little more on PC trees and PQR trees.}

We will see more of \PQRtree in Section~\ref{sec:surveycertalgo}

\temptext{
  \begin{enumerate}[ -I-]
  \item  Variations - PQR, PC etc. [MM96, Hsu01, McC04]\\
    Generalized PQ trees McC04 - brief. Will be elaborated in
    Section~\ref{sec:surveycertalgo}\\
    Hsu also invented PC trees \cite{wlh01}\tnote{This result first
      appeared inproc ISAAC92} which is claimed to be much easier to
    implement.
  \item Set theoretic characterizations [Hsu02, NS09]\\
    \cite{wlh02} describes the simpler algorithm for
    COT.\tnote[pressing]{in terms of what?}\\
    \cite{nsnrs09} describes a characterization of consecutive-ones
    property solely based on the cardinality properties of the set
    representations of the columns (rows); every column (row) is
    equivalent to a set that has the row (column) indices of the rows
    (columns) that have one entries in this column (row). This is
    interesting and relevant, especially to this thesis because it
    simplifies COT to a great degree by reducing the solution search
    space owing to the a simple set theoretic characterization.\\
  \item Parallel algorithms [AS95, BS03, CY91]
  \end{enumerate}
